\chapter{Research Questions}
\label{chap:research_questions}

% well-stated
% focused, concise
% feasible
% original
% at PhD level:  rigorous, publishable, sufficiently independent
% of appropriate scope

Given the gaps identified in the Literature Review, this PhD has the following Research Questions.

\vspace{12px}

\textit{\textbf{RQ1: How can we automatically reveal the framing differences in articles presenting the same event?}}

\vspace{12px}

This question focuses on how to develop a cross-article framing analysis that would overcome some of the limitations evidenced.
We can break it down in two sub-questions, one on the reader-side and the other on the technological side:

\begin{itemize}
    % \item \textbf{RQ1.1: Which methods do we need to reveal the framing and narrative differences?} This subquestion deals with the methods that we need to retrieve, analyse, combine and explore the connections between news articles. % literature review
    
    \item \textbf{RQ1.1: What is the contribution of comparing multiple articles to see framing signals?}
    % Which cross-article signals can we define to express the framing differences?
    % Which signals of framing can be identified from the comparison of multiple articles?
    We need to understand from the point of view of the reader how much important it is to have multiple articles available and compare them to be aware of the several framing techniques used. 
    % We need to define some tangible signals that represent how the framing of the articles is emerging through the use of language. % experimentation
    
    % \item \textbf{RQ1.3: Which features reveal framing intentionality of linguistic choices?} Choosing terms sometimes is done with a specific intention to evoke or amplify a certain point, sometimes it is not.\todo{merge with RQ1.2?}
    %  To what extent do they reveal biases with respect to just capturing different ways of expressing the same events?
    
    \item \textbf{RQ1.2: To what extent can we automatically recognise framing signals using multiple documents?}
    % To what extent can an automated framework recognise framing signals?
    % How would a cross-article automatic framing analysis perform?
    We want to investigate the impact of having multiple articles available on the ability of an automated method to identify and label framing differences.
    % Answering this question is very important to understand how ready would the framework be to spot the signals identified previously. % usefulness
    
\end{itemize}


\vspace{12px}

% \textit{\textbf{RQ2: How do stories change between news sources?}}\todo{change}
\textit{\textbf{RQ2: How do news sources with different characteristics change stories over time?}}

\vspace{12px}

This second question instead moves the emphasis on the sources where articles are published. We can break it down in two subquestions:

\begin{itemize}
    \item \textbf{RQ2.1: Which features of a news source influence the framing techniques used?}
    % How does the affiliation of a news source relate with the  framing techniques it uses?
    % How well does the framing analysis relate with the information available on affiliation, newsgroup and bias of the single outlets?
    News sources can be described by using their political alignment, the news group they belong to, their location, and we want to see if some of them are related to the amount and type of framing techniques that occur in their articles.
    
    \item \textbf{RQ2.2: To what extent can we identify the evolution of the framing of a certain event?}
    % To what extent can we identify cascades of information using temporal information?
    We aim at extracting temporised chains that track a specific event across news sources, from where it is seen the first time and how it evolves through time and sources.
    Can we identify some patterns that describe how the information flows between news sources?
    %How would this interact with rephrasing and other techniques that aim to avoid being spotted as plagiarism? (Linguistic variations vs semantics). And is temporal metadata reliable? (silent edits...)
    
    % \item \textbf{RQ2.2: What do these patterns tell us?} Do the patterns provide useful information and spot real % it has as assumption that there are patterns
    
    
\end{itemize}
