\chapter{Research Questions}

% well-stated
% focused, concise
% feasible
% original
% at PhD level:  rigorous, publishable, sufficiently independent
% of appropriate scope

Given the gap identified in the Literature Review, this PhD has the following Research Questions.

\vspace{12px}

\textit{\textbf{RQ1: How to automatically reveal the differences in articles presenting the same events?}}

\vspace{12px}

This question then breaks down into several subquestions:

\begin{itemize}
    \item \textbf{RQ1.1: Which methods do we need to reveal the framing and narrative differences?} This subquestion deals with the methods that we need to retrieve, analyse, combine and explore the connections between news articles.
    \item \textbf{RQ1.2: Which cross-article signals can we define to express the differences?} We need to define some tangible signals that represent how the framing of the articles is emerging through linguistic devices.
    \item \textbf{RQ1.3: Would these differences be meaningful? To what extent do they reveal biases with respect to just capturing different ways of expressing the same events?} Answering this question is very important to evaluate the scope of application of this work. It's both an analysis of what is common and what is unique of each articles, but then we also add an analysis to extract which framing differences exist.   
\end{itemize}


\vspace{12px}

\textit{\textbf{RQ2: How to identify patterns of information flow between news sources?}}

\vspace{12px}

\begin{itemize}
    \item \textbf{RQ2.1: To what extent can we identify cascades of information by bringing together the analysis of RQ1 with temporal information?}
    
    \item \textbf{How well does this analysis relate with the information available on News Groups and bias of the single outlets?}
    
\end{itemize}